Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2024-05-31 analysis/paper/paper.Rmd
Minor changes.

All regression coefficients are assumed to be Gaussian distributed, with
prior means from Johnson et al's (2020) regression model estimates (Table \@ref(tab:priors)). We
calibrated the standard deviations of the priors so that the 95% prior predictive
intervals for survival and recruitment from the Bayesian model match the
or exceed the 95% predictive intervals from Johnson et al's regression model (Supplement C, Figure
\@ref(fig:examplePredictions)).

@@

knitr::kable(tbl,caption="Prior means and standard deviations of Gaussian distributed survival and reproduction model parameters. Standard deviations are calibrated so that the 95\\% prior predictive intervals for survival and recruitment from the Bayesian model match the
or exceed the 95% predictive intervals from Johnson et al's regression model (Supplement C).")
```

>>>>

All regression coefficients are assumed to be Gaussian distributed, with
prior means from Johnson et al's (2020) regression model estimates (Table \@ref(tab:priors)). We
calibrated the standard deviations of the priors so that the the 95% prior predictive
intervals for survival and recruitment from the Bayesian model match the
95% predictive intervals from Johnson et al's regression model (Supplement C, Figure
\@ref(fig:examplePredictions)).

@@

knitr::kable(tbl,caption="Prior means and standard deviations of Gaussian distributed survival and reproduction model parameters. Standard deviations are calibrated so that the 95\\% prior predictive intervals for survival and recruitment from the Bayesian model match the
the 95% predictive intervals from Johnson et al's regression model (Supplement C).")
```
